A More Complete Algebra for File Synchronization

### 2015-11-09 2015/paper.tex
Fixed typos

We often encounter the case where we only have a set of commands without a sepcified order.
Indeed, it is actually the task of the reconciler to determine whether there is an order
in which updates from multiple replicas can all be applied to a filesystem.

@@

If $U$ is a minimal set of commands
that we know can be applied to at least one filesystem in some order without breaking it,
then we can split $U$ into a maximum number of disjunct subsets
(components) so that the paths of two commands from different subsets would never be directly related.
If we aim to order the commands in $U$, then we can focus on order the commands
inside the components, as all permutations of the components are allowed:
the commands in them will commute.

@@

In each component that is larger than one, the patch are directly related
and the commands form construction or destruction chains.
To order the commands,
select the command with the topmost path, so that there would be no command
on its parent path. If the command removes content at this path, the command
needs to follow all other commands in the component, and
the component is a destruction component.
Otherwise the command with the topmost component needs to precede other commands
in the component, and it is a construction component.
Repeat the above process of splitting commands into subsets on the remaining commands
in the component. Recursively, this way we can determine all allowed orders of the commands.

>>>>

We often encounter the case where we only have a set of commands without a specified order.
Indeed, it is actually the task of the reconciler to determine whether there is an order
in which updates from multiple replicas can be applied to a filesystem.

@@

If $U$ is a minimal set of commands
that we know can be applied to at least one filesystem in some order without breaking it,
then we can split $U$ into a maximum number of disjunct subsets
(components) so that the paths of two commands from different subsets would never be directly related.
If we aim to order the commands in $U$, then we can focus on ordering the commands
inside the components, as all permutations of the components are allowed:
the commands in them will commute.

@@

In each component that is larger than one, the paths are directly related
and the commands form construction or destruction chains.
To order the commands,
select the command with the topmost path, so that there would be no command
on its parent path. If the command removes content at this path, the command
needs to follow all other commands in the component, and
the component is a destruction component.
Otherwise the command with the topmost component needs to precede other commands
in the component, and it is a construction component.
Repeat the above process of splitting commands into subsets on the remaining commands
in the component. Recursively, this way we can determine all allowed orders of the commands.
